Carbonate chemistry at Ny-Ålesund

### 2021-03-15 awipev-CO2.Rmd
Finalized section on choice of K, K2

## Impact of choice of constants
### Using mean values
```{r impact of constants 1, echo=FALSE, warning=FALSE, message=FALSE}
# Compare Lueker and Sulpis
# use mean values calculated for impacts of nutrients above
means <- d_all %>% 
  group_by(montht) %>% 
  summarize(mean_ct = mean(ct, na.rm = TRUE),
            mean_at_calc = mean(at_calc, na.rm = TRUE),
            mean_pco2_calc = mean(pco2_calc_fb, na.rm = TRUE),
            mean_sal = mean(sal_fb, na.rm = TRUE),
            mean_temp = mean(temp_fb, na.rm = TRUE)) %>% 
  ungroup()
mean_ct <-  mean(means$mean_ct)
mean_at_calc <-  mean(means$mean_at_calc)
mean_pco2_calc <-  mean(means$mean_pco2_calc)
mean_sal <-  mean(means$mean_sal)
mean_temp <-  mean(means$mean_temp)
# impacts using pco2 and AT
carb_l_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0, 
                 Pt = 0, Sit = 0,
                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
carb_s_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0, 
                 Pt = 0, Sit = 0,
                 k1k2 = "s20", kf = "dg", ks = "d", pHscale = "T", b = "u74")
diff_ls_1 <- carb_l_1 - carb_s_1

# impacts using AT-DIC pair
carb_l_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0, 
                 Pt = 0, Sit = 0,
                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
carb_s_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0,
                Pt = 0, Sit = 0, 
                k1k2 = "s20", kf = "dg", ks = "d", pHscale = "T", b = "u74")
diff_ls_2 <- carb_l_2 - carb_s_2
const <- bind_rows(diff_ls_1, diff_ls_2) %>% 
  dplyr::mutate(flag = c("pCO2 and ALK", "ALK and DIC"),
                S = mean_sal,
                T = mean_temp,
                DIC = DIC * 1e6
                ) %>% 
  dplyr::select(flag:T, pH, pCO2, DIC, OmegaAragonite)
#kable(const, digits = c(0, 1, 1, 3, 1, 1, 2))
pander(const)
```
### Using all values pCO2 and at_calc

```{r impact of constants 2, echo=FALSE, warning=FALSE, message=FALSE}
# Compare Lueker and Sulpis
d_ls <- d_all %>% 
  drop_na(pco2_fb, at_calc, sal_fb, temp_fb)
carb_l <-
  carb(
    24,
    d_ls$pco2_fb,
    d_ls$at_calc * 1e-6,
    S = d_ls$sal_fb,
    T = d_ls$temp_fb,
    P = 0,
    Pt = 0,
    Sit = 0,
    k1k2 = "l",
    kf = "dg",
    ks = "d",
    pHscale = "T",
    b = "u74"
  )
carb_s <-
  carb(
    24,
    d_ls$pco2_fb,
    d_ls$at_calc * 1e-6,
    S = d_ls$sal_fb,
    T = d_ls$temp_fb,
    P = 0,
    Pt = 0,
    Sit = 0,
    k1k2 = "s20",
    kf = "dg",
    ks = "d",
    pHscale = "T",
    b = "u74"
  )
diff_ls <- as_tibble(carb_l - carb_s)
d_ls <- bind_cols(d_ls, diff_ls)

>>>>

## Impact of choice of constants
### Lueker vs Sulpis using mean values
```{r impact of constants 1, echo=FALSE, warning=FALSE, message=FALSE}
# Compare Lueker and Sulpis
# use mean values calculated for impacts of nutrients above
monthly_means <- d_all %>% 
  group_by(montht) %>% 
  summarize(mean_ct = mean(ct, na.rm = TRUE),
            mean_at_calc = mean(at_calc, na.rm = TRUE),
            mean_pco2_calc = mean(pco2_calc_fb, na.rm = TRUE),
            mean_sal = mean(sal_fb, na.rm = TRUE),
            mean_temp = mean(temp_fb, na.rm = TRUE)) %>% 
  ungroup()
mean_ct <-  mean(monthly_means$mean_ct)
mean_at_calc <-  mean(monthly_means$mean_at_calc)
mean_pco2_calc <-  mean(monthly_means$mean_pco2_calc)
mean_sal <-  mean(monthly_means$mean_sal)
mean_temp <-  mean(monthly_means$mean_temp)
# impacts using pco2 and AT pair
carb_l_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0, 
                 Pt = 0, Sit = 0,
                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
carb_s_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0, 
                 Pt = 0, Sit = 0,
                 k1k2 = "s20", kf = "dg", ks = "d", pHscale = "T", b = "u74")
diff_ls_1 <- carb_l_1 - carb_s_1

# impacts using AT-DIC pair
carb_l_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0, 
                 Pt = 0, Sit = 0,
                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
carb_s_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0,
                Pt = 0, Sit = 0, 
                k1k2 = "s20", kf = "dg", ks = "d", pHscale = "T", b = "u74")
diff_ls_2 <- carb_l_2 - carb_s_2
const_choice <- bind_rows(diff_ls_1, diff_ls_2) %>% 
  dplyr::mutate(flag = c("pCO2 and ALK", "ALK and DIC"),
                S = mean_sal,
                T = mean_temp,
                DIC = DIC * 1e6
                ) %>% 
  dplyr::select(flag, T, pH, pCO2, DIC, OmegaAragonite)
#kable(const, digits = c(0, 1, 1, 3, 1, 1, 2))
pander(const_choice)
```
### Lueker vs Sulpis using all values pCO2 and at_calc

```{r impact of constants 2, echo=FALSE, warning=FALSE, message=FALSE}
# Compare Lueker and Sulpis
tmp <- d_all %>% 
  drop_na(pco2_fb, at_calc, sal_fb, temp_fb)
carb_l <-
  carb(
    24,
    tmp$pco2_fb,
    tmp$at_calc * 1e-6,
    S = tmp$sal_fb,
    T = tmp$temp_fb,
    P = 0,
    Pt = 0,
    Sit = 0,
    k1k2 = "l",
    kf = "dg",
    ks = "d",
    pHscale = "T",
    b = "u74"
  )
carb_s <-
  carb(
    24,
    tmp$pco2_fb,
    tmp$at_calc * 1e-6,
    S = tmp$sal_fb,
    T = tmp$temp_fb,
    P = 0,
    Pt = 0,
    Sit = 0,
    k1k2 = "s20",
    kf = "dg",
    ks = "d",
    pHscale = "T",
    b = "u74"
  )
diff_ls <- as_tibble(carb_l - carb_s) %>% 
  dplyr::select(pH, pCO2, DIC, OmegaAragonite)
a
dplyr::mutate
diff_ls_quant <- bind_rows(
  quantiles(diff_ls$pH),)
)
const_choice <- bind_rows(diff_ls_1, diff_ls_2) %>% 
  dplyr::mutate(flag = c("pCO2 and ALK", "ALK and DIC"),
                S = mean_sal,
                T = mean_temp,
                DIC = DIC * 1e6
                ) %>%
